\textbf{\glsfmtfull{ris}:\\Beamforming, Modulation, and Channel Shaping}

### 2024-05-18 content/chapter_6.tex
:triangular_flag_on_post: Minor amendment 240518

\begin{section}{Future Works}
	Many interesting problems are countered during the research but not fully addressed due to time constraints, to name a few:
	\begin{itemize}
		\item \emph{\gls{ris}-aided multi-user \gls{swipt}:} Extension to multi-user scenario is non-trivial because (i) the waveform and passive beamforming are shared among users while the active beamforming and power splitting ratios are user-specific; (ii) the interference can be harvested for power purpose such that dedicated information and power precoders are desired; (iii) due to harvester nonlinearity, the optimal design is highly non-convex and depends heavily on the multiple access scheme; (iv) a proper criterion is needed to cover the \gls{r-e} trade-off and fairness among users.
		\item \emph{Capacity region of RIScatter:} The current work considers a decoding order from backscatter to primary, corresponding to a primary-optimal point (but not a corner due to energy detector) in the capacity region.
		If the primary message can be decoded first, it can be modelled as a spreading sequence that enhances the backscatter \gls{snr} by $N$ times (where $N$ is the symbol period ratio) \cite{Long2020a}, corresponding to a backscatter-optimal point.
		Besides, the backscatter detection can be performed coherently in the signal domain to further improve the achievable rate.
		\item \emph{RIScatter, index modulation, and rate splitting:} In RIScatter, the primary and backscatter symbols are superimposed by multiplicative coding, and the nodes usually have a finite number of reflection states. Instead of acting as a pure channel controller or individual information source, a \gls{ris} can be integrated into the \gls{rf} transmitter as an additional index modulator to enhance the spectral efficiency \cite{Basar2020}.
		The transmitted message is thus split into an amplitude-phase modulated component and an index-modulated component, which can be decoded separately at the receiver \cite{Zhong2018}. This could further improve the capacity of \gls{ris}-aided \gls{mimo} systems \cite{Ye2022}, or make a low-complexity realization of \gls{rsma} \cite{Mao2018} in a multi-user system where the reflection pattern conveys the common message.
		\item \emph{RIScatter and sensing:} The proposed RIScatter concept can be extended to sensing applications, where the scatter nodes are equipped with sensors to monitor the environment and report the information to the \gls{ap}. The challenge is to design the input distribution and reflection states to stabilize the environment for improved sensing performance while guaranteeing the communication quality.
		\item \emph{\gls{bd}-\gls{ris} and frequency shifting:} Similar to \gls{ambc}, the different groups of \gls{bd}-\gls{ris} can be used to shift the incident wave to different frequencies.
		This phenomenon can be exploited to mitigate the self and inter-operator interference \cite{Miridakis2024}, generate a multi-frequency signal out of a \gls{cw}, or manipulate the response of frequency-selective channels. However, it could be challenging to design and implement the time-varying scattering matrices at a low power consumption.
		\item \emph{Multi-sector \gls{bd}-\gls{ris} and interference alignment:} The current work solves leakage interference minimization and \gls{wsr} maximization problems in \gls{ris}-aided \gls{ic}.
		It remains unknown how many scattering elements are required to completely eliminate the interference, and what is the \gls{dof} in a $K$-user $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ \gls{ic}.
		Besides, there exists a multi-sector model \cite{Li2023c} that provides full-space coverage and highly directional beams.
		It would be interesting to see how those sector-specific (instead of being shared by all users) scattering matrices can help to align the interference and improve the fairness issue.
	\end{itemize}
\end{section}

>>>>

\begin{section}{Future Works}
	Many interesting problems are countered during the research but not fully addressed due to time constraints, to name a few:
	\begin{itemize}
		\item \emph{\gls{ris}-aided multi-user \gls{swipt}:} Extension to multi-user scenario is non-trivial because (i) the waveform and passive beamforming are shared among users while the active beamforming and power splitting ratios are user-specific; (ii) the interference can be harvested for power purpose such that dedicated information and power precoders are desired; (iii) due to harvester nonlinearity, the optimal design is highly non-convex and depends heavily on the multiple access scheme; (iv) a proper criterion is needed to cover the \gls{r-e} trade-off and fairness among users.
		\item \emph{Capacity region of RIScatter:} The current work considers a decoding order from backscatter to primary, corresponding to a primary-optimal point (but not a corner due to energy detector) in the capacity region.
		If the primary message can be decoded first, it can be modeled as a spreading sequence that enhances the backscatter \gls{snr} by $N$ times (where $N$ is the symbol period ratio) \cite{Long2020a}, corresponding to a backscatter-optimal point.
		Besides, the backscatter detection can be performed coherently in the signal domain to further improve the achievable rate.
		\item \emph{RIScatter, index modulation, and rate splitting:} In RIScatter, the primary and backscatter symbols are superimposed by multiplicative coding, and the nodes usually have a finite number of reflection states. Instead of acting as a pure channel controller or individual information source, a \gls{ris} can be integrated into the \gls{rf} transmitter as an additional index modulator to enhance the spectral efficiency \cite{Basar2020}.
		The transmitted message is thus split into an amplitude-phase modulated component and an index-modulated component, which can be decoded separately at the receiver \cite{Zhong2018}. This could further improve the capacity of \gls{ris}-aided \gls{mimo} systems \cite{Ye2022}, or make a low-complexity realization of \gls{rsma} \cite{Mao2018} in a multi-user system where the reflection pattern conveys the common message.
		\item \emph{RIScatter and sensing:} The proposed RIScatter concept can be extended to sensing applications, where the scatter nodes are equipped with sensors to monitor the environment and report the information to the \gls{ap}. The challenge is to design the input distribution and reflection states to stabilize the environment for improved sensing performance while guaranteeing the communication quality.
		\item \emph{\gls{bd}-\gls{ris} and frequency shifting:} Similar to \gls{ambc}, the different groups of \gls{bd}-\gls{ris} can be used to shift the incident wave to different frequencies.
		This phenomenon can be exploited to mitigate the self and inter-operator interference \cite{Miridakis2024}, generate a multi-frequency signal out of a \gls{cw}, or manipulate the response of frequency-selective channels. However, it could be challenging to design and implement the time-varying scattering matrices at a low power consumption.
		\item \emph{Multi-sector \gls{bd}-\gls{ris} and interference alignment:} The current work solves leakage interference minimization and \gls{wsr} maximization problems in \gls{ris}-aided \gls{ic}.
		It remains unknown how many scattering elements are required to completely eliminate the interference, and what is the \gls{dof} in a $K$-user $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ \gls{ic}.
		Besides, there exists a multi-sector model \cite{Li2023c} that provides full-space coverage and highly directional beams.
		It would be interesting to see how those sector-specific (instead of being shared by all users) scattering matrices can help to align the interference and improve the fairness issue.
	\end{itemize}
\end{section}

### 2024-05-18 viva/slides.tex
:sparkles: Add lite slides
:construction: Fix typos
:triangular_flag_on_post: Minor amendment 240518

\newacronym{fsss}{FSSS}{Frequency-Hopping Spread Spectrum}

@@

	\begin{frame}{Signal model}
		\begin{figure}[H]
			\centering
			\def\svgwidth{0.6\columnwidth}
			\input{../assets/viva/riscatter_network.pdf_tex}
			\label{fg:riscatter_network}
		\end{figure}
		Within each backscatter block, received signal at primary block $n$ is
		\begin{equation*}
			y[n] = \underbrace{\mathbf{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} \textcolor{orange}{x_k}}_{\mathbf{h}^\mathsf{H}(\textcolor{orange}{x_{\mathcal{K}}})} \mathbf{w} \textcolor{blue}{s[n]} + v[n],
		\end{equation*}
		\vspace{-0.25cm}
		\begin{block}{Properties}
			\begin{enumerate}
				\item \textcolor{blue}{Primary} and \textcolor{orange}{backscatter} symbols are superimposed by {double modulation}
				\item Backscatter signal is much weaker due to {double fading}
				\item The spreading factor (i.e., symbol period ratio $N$) is usually large
				\item Each {state} is simultaneously part of information and beamforming {codeword}
				\item Reflection pattern over time is guided by input probability distribution
			\end{enumerate}
		\end{block}
	\end{frame}

	\begin{frame}{Low-Complexity Receiver}
		We propose a low-complexity receiver that exploits the aforementioned properties to avoid \gls{sic}.
		\begin{figure}[!t]
			\centering
			\subfloat{
				\resizebox{0.42\linewidth}{!}{
					\input{../assets/viva/receiver.tex}
				}
			}
			\subfloat{
				\resizebox{0.58\linewidth}{!}{
					\input{../assets/viva/energy_distribution.tex}
				}
			}
			\label{fg:receiver}
		\end{figure}
		\vspace{0.5cm}
		\begin{itemize}
			\item Accumulated receive energy $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ follows Gamma distribution
			\item \textcolor{orange}{Backscatter detection} under primary uncertainty is part of \textcolor{blue}{channel training}
			\item Requires one energy comparison and re-encoding per backscatter symbol (much simpler than symbiotic radio with $N$ \gls{sic} and 1 combining)
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Future works: III}
		\begin{block}{Feasibility of interference alignment by \gls{ris}}
			\begin{align*}
				&\text{find} && \mathbf{\Theta} &&&\\
				&\text{s.t.} && \mathbf{H}^{[kj]} = \mathbf{H}_\mathrm{D}^{[kj]} + \mathbf{H}_\mathrm{B}^{[k]} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{[j]} = \mathbf{0}, &&& \forall j \neq k\\
				& && \mathrm{rank}(\mathbf{H}^{[kk]}) = d_k, &&& \forall k
			\end{align*}
			\begin{itemize}
				\item Necessary and sufficient feasibility conditions?
				\item How many scattering elements are required on expectation?
				\item Multi-sector \gls{bd}-\gls{ris} \cite{Li2023c}?
			\end{itemize}
		\end{block}
	\end{frame}

\end{section}
% \end{section}

% \begin{section}{Research Proposal}
% 	\begin{subsection}{STAR-RIS: Interference Alignment}
% 		\begin{frame}{STAR-RIS in Interference Channel (I)}
% 			Consider a STAR-RIS-aided interference \gls{mimo} of $K$ transmitter-receiver pairs.
% 			\begin{block}{Leakage interference minimization}
% 				\vspace{-2em}
% 				\begin{mini!}
% 					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \bigl\lVert \mathbf{G}_k \underbrace{(\mathbf{H}^{[kj]}_\mathrm{D} + \mathbf{H}^{[k]}_\mathrm{B} \mathbf{\Theta}^{[kj]} \mathbf{H}^{[j]}_{\mathrm{F}})}_{\triangleq \mathbf{H}^{[kj]}} \mathbf{W}_j \bigr\rVert _{\mathrm{F}}^2}{\label{op:leakage}}{}
% 					\addConstraint{\mathbf{\Theta}_{\mathrm{T},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{T},g}+\mathbf{\Theta}_{\mathrm{R},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{R},g}=\mathbf{I}, \quad}{\forall g}{\label{co:scatter}}
% 					\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad}{\forall k}{\label{co:combiner}}
% 					\addConstraint{\mathbf{W}_j^\mathsf{H} \mathbf{W}_j=\mathbf{I}, \quad}{\forall j,}{\label{co:precoder}}
% 				\end{mini!}
% 			\end{block}

% 			\begin{block}{Feasibility of interference alignment}
% 				\vspace{-1em}
% 				\begin{subequations}
% 					\begin{align}
% 						&\text{find} && \mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\} &&&\\
% 						&\text{s.t.} && \mathbf{G}_k \mathbf{H}^{[kj]} \mathbf{W}_j = \mathbf{0}, &&& \forall j \neq k\\
% 						& && \mathrm{rank}(\mathbf{G}_k \mathbf{H}^{[kk]} \mathbf{W}_k) = d_k, &&& \forall k
% 					\end{align}
% 				\end{subequations}
% 			\end{block}
% 		\end{frame}

% 		\begin{frame}{STAR-RIS in Interference Channel (II)}
% 			\begin{block}{Weighted sum-rate maximization}
% 				\vspace{-2em}
% 				\begin{maxi!}
% 					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{\sum_k \rho_k \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{[kj]}}^\mathsf{H} \mathbf{Q}_k^{-1} {\mathbf{H}^{[kj]}} \mathbf{W}_k\biggr)}{\label{op:ic_rate}}{\label{ob:ic_rate}}
% 					\addConstraint{\mathbf{\Theta}_{\mathrm{T},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{T},g}+\mathbf{\Theta}_{\mathrm{R},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{R},g}=\mathbf{I}, \quad}{\forall g}{}
% 					\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k, \quad}{\forall k,}{}
% 				\end{maxi!}
% 				where $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix at receiver $k$
% 				\begin{equation*}
% 					\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} {\mathbf{H}^{[kj]}}^\mathsf{H} + \eta \mathbf{I},
% 				\end{equation*}
% 			\end{block}
% 		\end{frame}
% 	\end{subsection}

% 	\begin{subsection}{NOMA: Index Modulation}
% 		\begin{frame}{\glsfmtlong{im} is a Multiplicative NOMA}
% 			\begin{block}{Multiplicative broadcast channel}
% 				The received signal is
% 				\begin{equation*}
% 					y_k = h_k \prod_q x_q + n.
% 				\end{equation*}
% 				\begin{itemize}
% 					\item \gls{sic} $\to$ successive channel refinement (better symbol-level precoding)
% 					\item \textcolor{blue}{Log-normal} is also maximum entropy distribution
% 					\item Product of log-normal is log-normal
% 				\end{itemize}
% 			\end{block}

% 			\begin{exampleblock}{Index modulation is a special case with superuser $R = R_1 + R_2$}
% 				\begin{itemize}
% 					\item $x_1 \sim \mathcal{CN}(0, \sigma_1^2)$ and $x_2$ with finite support
% 					\item Index message encoded in the Euclidean distance between $h x_2^{(i)}$
% 					\item Decode $x_2$ first, rate depends on \textcolor{blue}{entropy of Gaussian mixture}
% 				\end{itemize}
% 			\end{exampleblock}
% 		\end{frame}

% 		\begin{frame}{Multiplicative NOMA: Another Example}
% 			\begin{block}{Joint transmitter-\gls{ris} encoding}
% 				The received signal is
% 				\begin{equation*}
% 					y_k = h_k \theta \sum_q x_q + n.
% 				\end{equation*}
% 				\vspace{-1em}
% 				\begin{itemize}
% 					\item Dynamic \gls{ris} can achieve the convex hull of static \gls{ris} \cite{Mu2021a}
% 					\begin{figure}
% 						\centering
% 						\subfloat{
% 							\resizebox{0.4\columnwidth}{!}{
% 								\includegraphics[scale=1]{assets/rate_region_noma.jpg}
% 							}
% 						}
% 						\subfloat{
% 							\resizebox{0.4\columnwidth}{!}{
% 								\includegraphics[scale=1]{assets/rate_region_oma.jpg}
% 							}
% 						}
% 					\end{figure}
% 					\item Joint encoding rides additional information on $\theta$ as ``common message''
% 				\end{itemize}
% 			\end{block}
% 		\end{frame}
% 		\begin{frame}{Thank You}
% 			\begin{figure}
% 				\centering
% 				\includegraphics[width=0.8\columnwidth]{assets/ris.jpg}
% 			\end{figure}
% 		\end{frame}
% 	\end{subsection}
% \end{section}

\bibliographystyle{IEEEtran}
\bibliography{../misc/library.bib}
\end{document}

>>>>

\newacronym{fhss}{FHSS}{Frequency-Hopping Spread Spectrum}

@@

	\begin{frame}{Signal model}
		\begin{figure}[H]
			\centering
			\def\svgwidth{0.6\columnwidth}
			\input{../assets/viva/riscatter_network.pdf_tex}
			\label{fg:riscatter_network}
		\end{figure}
		Within each backscatter block, received signal at primary block $n$ is
		\begin{equation*}
			y[n] = \underbrace{\Bigl(\mathbf{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} \textcolor{orange}{x_k}\Bigr)}_{\mathbf{h}^\mathsf{H}(\textcolor{orange}{x_{\mathcal{K}}})} \mathbf{w} \textcolor{blue}{s[n]} + v[n],
		\end{equation*}
		\vspace{-0.25cm}
		\begin{block}{Properties}
			\begin{enumerate}
				\item \textcolor{blue}{Primary} and \textcolor{orange}{backscatter} symbols are superimposed by {double modulation}
				\item Backscatter signal is much weaker due to {double fading}
				\item The spreading factor (i.e., symbol period ratio $N$) is usually large
				\item Each {state} is simultaneously part of information and beamforming {codeword}
				\item Reflection pattern over time is guided by input probability distribution
			\end{enumerate}
		\end{block}
	\end{frame}

	\begin{frame}{Low-complexity receiver}
		We propose a low-complexity receiver that exploits the aforementioned properties to avoid \gls{sic}.
		\begin{figure}[!t]
			\centering
			\subfloat{
				\resizebox{0.42\linewidth}{!}{
					\input{../assets/viva/receiver.tex}
				}
			}
			\subfloat{
				\resizebox{0.58\linewidth}{!}{
					\input{../assets/viva/energy_distribution.tex}
				}
			}
			\label{fg:receiver}
		\end{figure}
		\vspace{0.5cm}
		\begin{itemize}
			\item Accumulated receive energy $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ follows Gamma distribution
			\item \textcolor{orange}{Backscatter detection} under primary uncertainty is part of \textcolor{blue}{channel training}
			\item Requires one energy comparison and re-encoding per backscatter symbol (much simpler than symbiotic radio with $N$ \gls{sic} and 1 combining)
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Future works: IV}
		\begin{block}{Feasibility of interference alignment by \gls{ris}}
			\begin{align*}
				&\text{find} && \mathbf{\Theta} &&&\\
				&\text{s.t.} && \mathbf{H}^{[kj]} = \mathbf{H}_\mathrm{D}^{[kj]} + \mathbf{H}_\mathrm{B}^{[k]} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{[j]} = \mathbf{0}, &&& \forall j \neq k\\
				& && \mathrm{rank}(\mathbf{H}^{[kk]}) = d_k, &&& \forall k
			\end{align*}
			\begin{itemize}
				\item Necessary and sufficient feasibility conditions?
				\item How many scattering elements are required on expectation?
				\item Multi-sector \gls{bd}-\gls{ris} \cite{Li2023c}?
			\end{itemize}
		\end{block}
	\end{frame}

\end{section}
\bibliographystyle{IEEEtran}
\bibliography{../misc/library.bib}
\end{document}
